---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->


[![CRAN
status](https://www.r-pkg.org/badges/version/posterior)](https://CRAN.R-project.org/package=posterior)
[![R build status](https://github.com/MansMeg/posteriordb/workflows/R-CMD-check/badge.svg)](https://github.com/MansMeg/posteriordb/actions)
[![codecov](https://codecov.io/gh/MansMeg/posteriordb/branch/master/graph/badge.svg)](https://codecov.io/gh/MansMeg/posteriordb)

# `posteriordb`: a database of Bayesian posterior inference

## What is `posteriordb`?

`posteriordb` is a set of posteriors, i.e. Bayesian statistical models and data sets, reference implementations in probabilistic programming languages, and reference posterior inferences in the form of posterior samples.

## Why use `posteriordb`?

`posteriordb` is designed to test inference algorithms across a wide range of models and data sets.  Applications include testing for accuracy, testing for speed, and testing for scalability.  Algorithms being tested may be approximate like variational inference or asymptotically exact like Markov chain Monte Carlo.  `posteriordb` can be used to test new algorithms being developed or deployed as part of continuous integration for ongoing regression testing of algorithms in probabilistic programming frameworks.

`posteriordb` also makes it easy for students and instructors to access a range of pedagogical and real-world examples with precise model definitions, well-curated data sets, and reference posteriors.

`posteriordb` is framework agnostic and easily accessible from R and Python.

For more details regarding the use cases of  `posteriordb`, see [doc/use_cases.md](https://github.com/MansMeg/posteriordb/blob/master/doc/use_cases.md).




## Content

See [DATABASE_CONTENT.md](https://github.com/MansMeg/posteriordb/blob/master/doc/DATABASE_CONTENT.md) for the details content of the posterior database.

## Contributing

We are happy with any help in adding posteriors, data, and models to the database! See [CONTRIBUTING.md](https://github.com/MansMeg/posteriordb/blob/master/doc/CONTRIBUTING.md) for the details on how to contribute.


## Quick usage of the posterior database from R

Install the package from GitHub

```{r, eval = FALSE}
remotes::install_github("MansMeg/posteriordb", subdir = "rpackage")
```

Load the R package and load a posterior from the default posteriordb.

```{r}
library(posteriordb)
pd <- pdb_default() # Posterior database connection
pn <- posterior_names(pd)
head(pn)
```

```{r}
po <- pdb_posterior("eight_schools-eight_schools_centered", pdb = pd)
po
```

From the posterior, we can easily access data and models as

```{r}
sc <- pdb_stan_code(x = po)
sc
```

We can get additional information about the model by using `info()`.

```{r}
info(sc)
```

To access data for a specific posterior, we can use `pdb_data()`

```{r}
dat <- pdb_data(po)
dat
```

Again, we can get additional information about the data by using `info()`.

```{r}
info(dat)
```

Finally, we can access reference posterior draws for the given posterior.

```{r}
rpd <- reference_posterior_draws(po)
```

The posterior is based on the [posterior](https://github.com/jgabry/posterior) R package structure and can easily be summarized and transformed using the `posterior` R package.

```{r}
library(posterior)
summarize_draws(rpd)
```

Using `info()`, we can access more detailed information on the reference posterior draws.

```{r}
info(rpd)
```

It is also possible to access only information for models, data, and draws as follows.

```{r}
pdb_model_info(po)
pdb_data_info(po)
pdb_reference_posterior_draws_info(po)
```

## Using the posterior database from python
See [python README](./python/README.md)

## Using the posterior database from R (extensive)
See [R README](./rpackage/README.md)

## Design choices (so far)

The main focus of the database is simplicity, both in understanding and in use.

The following are the current design choices in designing the posterior database.

1. Priors are hardcoded in model files as changing the prior changes the posterior.
   Create a new model to test different priors.
1. Data transformations are stored as different datasets.
   Create new data to test different data transformations, subsets, and variable settings. This design choice makes the database larger/less memory efficient but simplifies the analysis of individual posteriors.
1. Models and data has (model/data).info.json files with model and data specific information.
1. Templates for different JSONs can be found in content/templates and schemas in schemas (Note: these don't exist right now and will be added later)
1. Prefix 'syn_' stands for synthetic data where the generative process is known and found in content/data-raw.
1. All data preprocessing is included in content/data-raw.
1. Specific information for different PPL representations of models is included in the PPL syntax files as comments, not in the model.info.json files.
